### 2020-01-04 Draft/Draft.tex
figure 11 added

>>>>

\centering\includegraphics[width=78mm]{{Fig11}.png}
\caption{{\small \textsf{RMSE} statistics from figure \ref{fig:10} mapped onto an ordinal \tit{truth value} space, i.e. \tit{better} or \tit{worse} than the \textsf{WCDA}. In this context, large positive and small negative values are mapped onto `worse' while large negative values are mapped onto `better'; the left panel shows the atmospheric component while the right panel depicts the ocean.}}
\label{fig:11}
